InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-29 paper.tex
Fix typo

The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 finetuned on the AI or Not dataset. swin-tiny-patch4-window7-224 by microsoft is a new vision Transformer \cite{liu2021swin}.

>>>>

The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset. Swin-Transformer by Microsoft is a new Vision Transformer which makes use of hierarchical windows. This reduces the self-attention to not-overlapping windows of other areas of the image \cite{liu2021swin}.
